---
title: "project1eda"
author: "JPR"
date: "28 de enero de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Course Project 1

Criteria

Was a valid GitHub URL containing a git repository submitted?
Does the GitHub repository contain at least one commit beyond the original fork?
Please examine the plot files in the GitHub repository. Do the plot files appear to be of the correct graphics file format?
Does each plot appear correct?
Does each set of R code appear to create the reference plot?


##Preparing data
```{r prepare data}

my.data <- read.table(file="household_power_consumption.txt", header=TRUE, sep=";", na.strings = "?", colClasses = c("character","character", rep("numeric",7)))

#Adequate classes
my.data$Date<-as.Date(my.data$Date, format="%d/%m/%Y")

# Subset dataset according the dates in study
my.data <- subset(my.data,Date >= as.Date("2007/2/1") & Date <= as.Date("2007-2-2"))


#Preparing more complete date
my.data$date2<-paste(my.data$Date,my.data$Time)
my.data$date2<-as.POSIXct(my.data$date2)

#Structure of data
str(my.data)


```

## Plot 1

```{r plot1}

hist(my.data$Global_active_power, main="Global Active Power", xlab = "Global Active Power (kilowatts)", col="red")

## Save
  dev.copy(png,"plot1.png", width=480, height=480)
  dev.off()

 
```


##Plot 2

```{r plot2}

plot(my.data$Global_active_power~my.data$date2, type="l", xlab="", ylab="Global Active Power (kilowatts)")

## Save 
  dev.copy(png,"plot2.png", width=480, height=480)
  dev.off()
```

##Plot 3

```{r plot3}

with(my.data, {
    
plot(Sub_metering_1~date2, type="l",xlab="", ylab="Global Active Power (kilowatts)")
    
    lines(Sub_metering_2~date2,col='Red')
    lines(Sub_metering_3~date2,col='Blue')

      })
  
legend("topright", col=c("black", "red", "blue"), lwd=c(1,1,1), 
         c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3"))
  
  #Save
  dev.copy(png, file="plot3.png", height=480, width=480)
  dev.off()
  
```

##Plot4

```{r plot4}

par(mfrow=c(2,2), mar=c(4,4,2,1), oma=c(0,0,2,0))
  with(my.data, {
    plot(Global_active_power~date2, type="l", ylab="Global Active Power (kilowatts)", xlab="")
      
    plot(Voltage~date2, type="l", ylab="Voltage (volt)", xlab="")
    plot(Sub_metering_1~date2, type="l", 
    xlab="",ylab="Global Active Power (kilowatts)")
    lines(Sub_metering_2~date2,col='Red')
    lines(Sub_metering_3~date2,col='Blue')
    legend("topright", col=c("black", "red", "blue"), lty=1, lwd=2, bty="n",
    legend=c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3"))
    plot(Global_reactive_power~date2, type="l", 
         ylab="Global Rective Power (kilowatts)",xlab="")
  })
  
  #Save
  dev.copy(png, file="plot4.png", height=480, width=480)
  dev.off()
  
  
```